---
title: "2020 Census Data Project"
author: "René Dario Herrera for Coconino County"
date: "11/29/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache=TRUE, comment=FALSE, dpi=150, echo=FALSE, message=FALSE, warning=FALSE)

# setup 
# packages 
library(here)
library(tidyverse)
library(tidycensus)
library(sf)
library(tmap)
library(tigris)

# options
options(tigris_use_cache = TRUE)

# get data 
# read county boundary 
county_boundary <- st_read(dsn = "../../gis_data/County_Boundary.geojson")
county_muni_boundaries <- st_read(dsn = "../../gis_data/County_Municipal_Boundaries.geojson")

# read data 
single_parent_by_gender <- read_rds("../data/single_parent_household_by_gender_plot.rds")
number_of_children <- read_rds("../data/number_of_children.rds")
number_of_seniors <- read_rds("../data/number_of_seniors.rds")
pop_by_age_chart <- read_rds("../data/age_group_summary_totals_plot.rds")
pop_by_age_spatial <- read_rds("../data/age_groups_spatial_summary_plot.rds")
housing_tenure_summary_spatial_plot <- read_rds("../data/housing_tenure_summary_spatial_plot.rds")
```

# Single parents and gender

```{r}
single_parent_by_gender
```

# Number of children

```{r}
number_of_children
```

# Number of Seniors

```{r}
number_of_seniors
```

# Population by Age Group 

```{r}
pop_by_age_chart
```

```{r}
pop_by_age_spatial
```

# Average income, broken out by gender, if possible

Not found in the 2010 Decennial Census.

# Employment, broken out further by gender

Not found in the 2010 Decennial Census.

# Number renting vs. owning vs. homeless

```{r}
housing_tenure_summary_spatial_plot
```

# Percent of housing units with more people than rooms (residential crowding)

Not found in the 2010 Decennial Census.

# Education level

Not found in the 2010 Decennial Census.

# Persons with no high school diploma (25+)

Not found in the 2010 Decennial Census.

# Households with no vehicle

Not found in the 2010 Decennial Census.